---
title: "Getting Started with dieroller"
author: "jilin cao"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to dieroller}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, echo = FALSE, message = FALSE}
knitr::opts_chunk$set(collapse = T, comment = "#>")
library(dieroller)
```

## Die Rolling

The package `"dieroller"` is a minimal implementation for simulating rolling
a die a given number of times, and to visualize the relative frequencies
in such a series of rolls.


## Creating a `die`

The first step is to create a `"die"` object with the function `die()`:

```{r}
mydie <- die()
mydie
```

By default, `die()` creates a _fair_ die with standard sides and with probability values.

You can change the defatuls with arguments `sides` and `prob`:

```{r}
die1 <- die(sides = c('i', 'ii', 'iii', 'iv', 'v', 'vi'))
die1
```


## Rolling a die

Once you have defined a `"die"` object, you can use the function `roll()` to
_roll_ a coin a given number of `times`. The output will be an object of class 
`"roll"`, which will contain the vector of `rolls`:

```{r}
roll50 <- roll(die1, times = 50)
roll50
```

The `summary()` function gives you a nice table of frequencies:
```{r}
summary(roll50)
```


## Plot of relative frequencies

You can use the function `plot()` to create a graohic with the relative 
frequencies of a series of die rolls:

```{r, fig.show='hold'}
plot(roll50)
```