---
title: "Hw03-jilin-cao"
author: "caojilin"
date: "3/16/2018"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,error=TRUE, fig.path = "./images/")
```

```{bash}

cut -d "," -f 2 nba2017-roster.csv | tail +2 | sort -u> team-names.txt
head -5 team-names.txt
```
```{bash}
cut -d "," -f 3 nba2017-roster.csv | tail +2 | sort -u> position-names.txt
cat position-names.txt
```
```{bash}
# I feel like "tail +2" ignores the first row and return rest of the table.
cut -d "," -f 7 nba2017-roster.csv | tail +2| sort -n |uniq -c > experience-counts.txt
head -5 experience-counts.txt
```


```{bash}
grep -E "LAC|team" nba2017-roster.csv > LAC.csv

cat LAC.csv

# No first row?
```

```{bash}
cut -d "," -f 6 LAC.csv |sort -n|uniq -c
```
```{bash}
grep "CLE" nba2017-roster.csv | wc -l
```

```{bash}
cut -d "," -f -2,4-5 nba2017-roster.csv  |grep -E "GSW|team"  > gsw-height-weight.csv
cat  gsw-height-weight.csv
# still no first row
```

```{bash}

grep "player" nba2017-roster.csv | cut -d "," -f 1,8 > top10-salaries.csv
cut -d "," -f -1,8 nba2017-roster.csv | sort -r -k2 -n -t, | head -10 >> top10-salaries.csv
cat top10-salaries.csv
#
#sed -i '' '1i\
#"player","salary"
#' top10-salaries.csv
```
1.Assume that the “successful” event is getting a “six” when rolling a die. Consider
rolling a fair die 10 times. Use bin_probability() to find the probability of getting
exactly 3 sixes.
```{r}
source('./code/binomial-functions.R')
bin_probability(10,3,1/6)

```
2.Use bin_distribution() to obtain the distribution of the number of “sixes” when
rolling a loaded die 10 times, in which the number “six” has probability of 0.25. Make
a plot of this distribution.
```{R}
# a loaded die with probability of "6" is 0.25
# p("6") = 0.25
dist = bin_distribution(10,0.25)
plot(x=dist[[1]],y=dist[[2]],xlab='success',ylab='probability',pch=18, col="blue",main = "binomial distribution of Binomial(10,0.25) ",cex.lab=1.25)
axis(1,at = seq(0,10,by=1),labels = seq(0,10,by=1))

```

3.Use bin_probability(), and a for loop, to obtain the probability of getting more
than 3 heads in 5 tosses with a biased coin of 35% chance of heads.
```{r}
prob = 0
for(i in 4:5){
  prob = prob + bin_probability(5,i,0.35)
}
prob
```
4.Use bin_distribution() to obtain the probability distribution of the number of heads
when tossing a loaded coin 15 times, with 35% chance of heads. Make a plot of this
distribution.

```{r}
library(ggplot2)
success = 0:15
probability = rep(0,16)
dat = bin_distribution(15,0.35)

#color outside the aes()

ggplot(data = dat,aes(x=success,y=probability)) +geom_point(color='dodgerblue3')+
  scale_x_continuous(breaks=pretty(dat$success,n=15))+scale_y_continuous(breaks=pretty(dat$probability,n=10))+
  theme_update(plot.title = element_text(hjust = 0.5))+ggtitle('distribution of Binomial(15,0.35)')

ggplot(dat,aes(x=success,y=probability))+geom_bar(stat = 'identity',col='dodgerblue3',fill='dodgerblue3')+labs(title="Binomail(15,0.35) distribution")
```
