---
title: "lab09-cao-jilin"
author: "caojilin"
date: "3/22/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,error=TRUE)
```
```{r}
states = rownames(USArrests)
nchar(states)
tolower(states)
toupper(states)
casefold(states,upper = TRUE)
casefold(states,upper = FALSE)

num_chars = nchar(states)

# frequency table
char_freqs = table(num_chars)
# barchart of number-of-characters
barplot(char_freqs)

paste(head(states),head(num_chars),sep = " = ")
paste(head(states),collapse = "")

substr("Berkeley",1,3)

#first three letters
first_three = substr(states,1,3)

#last three letters, without num_chars, it's hard to do so
last_three = substr(states,num_chars-2,num_chars)

#shorten state names with first 3 characters
paste0(substr(states,1,1),last_three)

#Challenge
states[num_chars==4]

states[num_chars==10]

paste(states[num_chars==4],collapse = ", ")

#Nice nice
states_list = list()
a = rownames(char_freqs)
a = as.integer(a)

for(i in a){
  if(i %% 2 == 0){
    states_list[[paste0(i,"-chars")]] = toupper(paste(states[num_chars==i],collapse = ", "))
  }else{
    states_list[[paste0(i,"-chars")]] = tolower(paste(states[num_chars==i],collapse = ", "))
  }
}
states_list



```

[google](www.google.com)
**Your turn**. Rewrite `temp_convert()` such that the argument to can be given in upper or lower case letters. *For instance*, the following three calls should be equivalent:
```{r}
to_celsius <- function(x = 1) {
  (x - 32) * (5/9)
}

to_kelvin <- function(x = 1) {
  (x + 459.67) * (5/9)
}

to_reaumur <- function(x = 1) {
  (x - 32) * (4/9)
}

to_rankine <- function(x = 1) {
  x + 459.67
}
temp_convert <- function(x = 1, to = "celsius") {
  to = tolower(to)
  switch(to,
         "celsius" = to_celsius(x),
         "kelvin" = to_kelvin(x),
         "reaumur" = to_reaumur(x),
         "rankine" = to_rankine(x))
}

temp_convert(30, 'celsius')
temp_convert(30, 'Celsius')
temp_convert(30, 'CELSIUS')
```
Imagine that you need to generate the names of 10 data .csv files. All the files have the same prefix name but each of them has a different number: file1.csv, file2.csv, ... , file10.csv.

How can you generate a character vector with these names in R? Come up with at least three different ways to get such a vector:
```{r}
name_list = 'file1.csv'
for(i in 2:10){
  name_list = c(name_list,paste0('file',i,'.csv')) 
}
name_list
# while loop
name_list2 = 'file1.csv'
i =  2
while(i <= 10){
  name_list2 = c(name_list2, paste0('file',i,'.csv') )
  i = i + 1
}
name_list2
#repeat

name_list3 = 'file1.csv'
i = 0
repeat{
  if(i == 11){
    return(name_list3)
  }
  name_list3 = c(name_list3,paste0('file',i,'.csv'))
  i = i+ 1
}
name_list3


# example: change prefix
# rename(c('file1.csv','file10.csv'),'dataset')
# output c('dataset1.csv','dataset10.csv')
rename = function(lst,change){
 #Or use gsub or sub, g stands for global
gsub('file',change,lst)
}
rename(name_list,'dataset')

```

```{r}
# name of output file
outfile <- "output.txt"

# ---
# title: "Some title"
# author: "Your name"
# date: "today's date"
# output: html_document
# ---

cat("---\n", file= outfile)
cat("title: no title \n", file= outfile,append = TRUE)
cat("author: caojilin \n", file= outfile,append = TRUE)
cat("date : 3/22 \n", file= outfile,append = TRUE)
cat("---\n\n\n", file= outfile,append = TRUE)

# writing to 'outfile.txt'
cat("This is the first line", file = outfile,append=TRUE)
# insert new line
cat("\n", file = outfile, append = TRUE)
cat("A 2nd line", file = "output.txt", append = TRUE)
# insert 2 new lines
cat("\n\n", file = outfile, append = TRUE)
cat("\nThe quick brown fox jumps over the lazy dog\n",
    file = outfile, append = TRUE)

```
##Valid Color Names

The function colors() returns a vector with the names (in English) of 657 colors available in R. Write a function is_color() to test if a given name---in English---is a valid R color. If the provided name is a valid R color, is_color() returns TRUE. If the provided name is not a valid R color is_color() returns FALSE.

```{r}
# your is_color() function
# you can use is.element(element,vector),  match(element,vector) returns the first position
# of such element in vector.
colors = colors()
is_color = function(string){
  # or use normal for loop to check every element.
  # if it is hashset it is fast.
  if(is.element(string,colors)){
    return(TRUE)
  }else{
    return(FALSE)
  }
}

# test it:
is_color('yellow')  # TRUE

is_color('blu')     # FALSE

is_color('turkuoise') # FALSE

colplot = function(col){
  if(is_color(col)){
    plot(runif(10,1,10),rnorm(10,1,10),main=paste0("Testing color ",col),col='blue',pch=19)
  }else{
    stop(paste0("Invalid color ", col))
  }
}
# this should plot
colplot('tomato')

# this stops with error message
colplot('tomate')
```

##Counting number of vowels
```{r}
# random vector of letters
set.seed(1)
letrs <- sample(letters, size = 100, replace = TRUE)
head(letrs)

count_vowel = function(lst){
  tem = lst[is.element(lst,c("a","e","i","o","u"))]
  return(table(tem))
}
count_vowel(letrs)

count_nonvowel = function(lst){
  tem = lst[!is.element(lst,c("a","e","i","o","u"))]
  return(table(tem))
}
count_vowel(letrs)
count_nonvowel(letrs)

# your function count_letters()
count_letters = function(vec){
  print(paste0("letters: ",length(vec)))
  print(paste0("vowels: ",sum(count_vowel(vec))))
  print(paste0("consonants: ",sum(count_nonvowel(vec))))

}
count_letters(letrs)
```